### 2015-11-06 CVPR16/Source/discussions.tex

Our experiments shows that our association probability produces more accurate
point to object associations when compared to bounding box based
association and state of art motion segmentation.
Also the localization experiment results show improvement by modeling occlusions, however, the average translation error of 5 meters is very high. Since the results are averaged over the entire KITTI dataset, there are various possible sources of error, including outliers in point tracks, outliers in detections results. 
One of the reasons of poor performance is that we set the parameters $\lambda_{\text{bbox,track,lane,dyn,size}}$ empirically which may be suboptimal. However, because of slow inference algorithms, which take about a day to run on 300 cores for the entire KITTI dataset, learning become infeasible.

>>>>

Our experiments show that our association probability produces more accurate
point to object associations when compared to bounding box based
association and state of art motion segmentation.
Also the localization experiment results show improvement in localization accuracy by modeling occlusions. However, the average translation error of 5 meters is very high. Since the results are averaged over the entire KITTI dataset, there are various possible sources of error, including outliers in point tracks, outliers in detections results. 
One of the reasons of poor performance is that we set the parameters $\lambda_{\text{bbox,track,lane,dyn,size}}$ empirically which may be suboptimal. However, because of slow inference algorithms, which take about a day to run on 300 cores for the entire KITTI dataset, learning become infeasible.
